---
title: "Week 3 Project"
author: "David Elliott"
date: "December 28, 2016"
output: html_document
---
## Closing the Gender Gap?
Shown are the annual average (1948-2016) unemployment rates for men and women, as reported by the US Bureau of Labor Statistics. Note that the 2016 average does not include the month of December.

```{r options}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r map}
library(htmltab)
data <- read.csv("book1.csv", header=TRUE)
data$Ann <- rowMeans(data[,2:13], na.rm = TRUE)
sexdata <- subset(data, Sex != "All")

library(plotly)
plot_ly(x = sexdata$Year, y = sexdata$Ann, color = sexdata$Sex, mode = 'lines') %>% layout(title = "Annual Average US Unemployment Rate",
         xaxis = list(title = "Year"),
         yaxis = list (title = "Unemployment Rate (%)"))
```

#### CREDIT: Data queried from US Bureau of Labor Statistics, https://data.bls.gov/cgi-bin/surveymost?ln

Original Series Downloaded were 1948-2016 (November):

* Unemployment Rate - 16-19 Years - LNS14000012

* Unemployment Rate - 20 Years & Over Men - LNS14000025

* Unemployment Rate - 20 Years & Over Women - LNS14000026

* Unemployment Rate - White - LNS14000003

* Unemployment Rate - Black or African American - LNS14000006

* Unemployment Rate - Asian - LNS14032183

* Unemployment Rate - Hispanic or Latino - LNS14000009